---
output:
  html_document: default
  pdf_document: default
---
# **Preliminary Analysis of Exp1-Overshadowing**
#### 3rd March 2020
*Mrudula*


Loading the libraries and setting up working directory
```{r Libraryloading, message=FALSE}
library(plyr)
library(tidyverse)
library(ez)
library(schoRsch)
library(lme4)
library(nlme)
library(data.table)

#removing workspace objects
rm(list = ls())


#home office setup
setwd("C:/FSU Jena_PhD/Exp1/Analysis")

#setwd("D:/PhD/Exp1-Overshadowing/Analysis")
```

Then the dataframe is loaded from the directory 
```{r}
Exp1data <- read.csv("C:/FSU Jena_PhD/Exp1/Data/Exp1data.csv")
#Exp1data <- read.csv("D:/PhD/Exp1-Overshadowing/Data/Exp1data.csv")
#removing the first column named x
Exp1data <- subset(Exp1data, select = -c(X))
#renaming first column to subject
names(Exp1data)[1] <- "Subject"
```

Preparing the data frame
* Creating two columns that contains the RT and ACC values
* Creating a new column with error rates
* Removing the values from the practice trials
```{r}
#creating 3 columns for RT and ACC and error rate
Exp1data$RT_Trial <- Exp1data$ExpDisplay.RT
Exp1data$ACC_Trial <- Exp1data$ExpDisplay.ACC
Exp1data$Errorrate <- (1 - Exp1data$ACC_Trial)*100

#removing practice trials
Exp1data <- Exp1data[!grepl("Practice", Exp1data$Condition),]
```

For ANOVA analysis to check for effect of salience and validity on test trials, learn trials are not required, hence removed
```{r}
 Exp1data <- Exp1data[!grepl("learn", Exp1data$Condition),]
```

Below you can find the summary of the Reaction Time data and calculating error percentage
```{r}
summary(Exp1data$RT_Trial)
table(Exp1data$ACC_Trial)
round(table(Exp1data$ACC_Trial)/nrow(Exp1data)*100, digits = 3)
```


### Removing RTs and Outliers

Outliers are computed on an **individual** level 

> Separate columns are created to modify RT values of individual farouts and individual outliers instead of changing it in the original RT_Trial column

Updated summary values after removing outliers/farouts are given below
```{r}
#removing the RT of the trials that were inaccurate
Exp1data$RT_Trial[Exp1data$ACC_Trial==0] <- NA

#summary after removing incorrect trials
summary(Exp1data$RT_Trial)

#OUtliers
#creating function to remove outliers and farouts
computeTukeys <- function(x){
  P25 <- quantile(x$RT, .25, na.rm = TRUE, type = 6) #type = 6 -> nimmt SPSS
  P75 <- quantile(x$RT, .75, na.rm = TRUE, type = 6)
  x$Outlier <- P75 + 1.5*(P75 - P25)
  x$Farouts <- P75 + 3.0*(P75 - P25)
  return(x)
}

#identifying RT farouts in the individual level
Exp1data <- ddply(Exp1data, .(Subject), computeTukeys)
summary(Exp1data$RT_Trial)

#creating new column with RT trials after removing outliers
Exp1data$RT_Trial_ifo <- Exp1data$RT_Trial
Exp1data$RT_Trial_io <- Exp1data$RT_Trial
Exp1data$RT_Trial_ifo[Exp1data$RT_Trial_ifo > Exp1data$Farouts|Exp1data$RT_Trial_ifo < 300] <- NA
Exp1data$RT_Trial_io[Exp1data$RT_Trial_io > Exp1data$Outlier|Exp1data$RT_Trial_io < 300] <- NA
summary(Exp1data$RT_Trial_ifo)
summary(Exp1data$RT_Trial_io)
```
Now, a dataframe is created that contains aggregate values of the RT per condition and one for Error rate 
```{r}
Exp1.aggdata_ifo <- aggregate(data=Exp1data, RT_Trial_ifo~Subject+Saliency+validity, mean)
Exp1.aggdata_io <- aggregate(data=Exp1data, RT_Trial_io~Subject+Saliency+validity, mean)
Exp1.aggdata_ER <- aggregate(data = Exp1data,Errorrate~Subject+Saliency+validity, mean)
#Exp1.aggdata_ifo$Errorrate <- Exp1.aggdata_ER$Errorrate

#Removing participant data that contain high error rates---must check with Carina if we have a threshold
# Exp1.aggdata_ifo <- Exp1.aggdata_ifo[!grepl(20, Exp1.aggdata_ifo$Subject),]
# Exp1.aggdata_ifo <- Exp1.aggdata_ifo[!grepl(11, Exp1.aggdata_ifo$Subject),]
# Exp1.aggdata_ifo <- Exp1.aggdata_ifo[!grepl(5, Exp1.aggdata_ifo$Subject),]


## changing the variables to factors for ANOVA analysis
Exp1.aggdata_ifo$Subject <- as.factor(Exp1.aggdata_ifo$Subject)
Exp1.aggdata_ifo$Saliency <- as.factor(Exp1.aggdata_ifo$Saliency)
Exp1.aggdata_ifo$validity <- as.factor(Exp1.aggdata_ifo$validity)

Exp1.aggdata_ER$Subject <- as.factor(Exp1.aggdata_ER$Subject)
Exp1.aggdata_ER$Saliency <- as.factor(Exp1.aggdata_ER$Saliency)
Exp1.aggdata_ER$validity <- as.factor(Exp1.aggdata_ER$validity)

write.csv(Exp1.aggdata_ifo, file="C:/FSU Jena_PhD/Exp1/Data/Exp1.aggdata_ifo.csv")
write.csv(Exp1.aggdata_io, file = "C:/FSU Jena_PhD/Exp1/Data/Exp1.aggdata_io.csv")
write.csv(Exp1.aggdata_ER, file = "C:/FSU Jena_PhD/Exp1/Data/Exp1.aggdata_ER.csv")

Exp1.aggdata_ifo <- read.csv("C:/FSU Jena_PhD/Exp1/Data/Exp1.aggdata_ifo.csv")
Exp1.aggdata_io <- read.csv("C:/FSU Jena_PhD/Exp1/Data/Exp1.aggdata_io.csv")
```


## Plotting the RT points to check for outliers and farouts
```{r distribution plots, out.width = "50%", fig.width=5, fig.height=3, fig.show='hold', fig.align='center'}
#first with farouts
ggplot(Exp1data, aes(x=validity, y=RT_Trial,color = Saliency))+
  geom_violin(alpha=0.2, position = position_dodge(1))+
  geom_jitter(alpha = 0.3, aes(color=Saliency), position = position_jitterdodge(.5))+
  geom_point(data = Exp1data, mapping = aes(x=validity, y=Farouts), type = "p", pch = 23, col = "cyan4", fill = "cyan4")+
  ggtitle("Distribution of RTs with farouts marked")+
  theme_bw()

#with outliers
ggplot(Exp1data, aes(x=validity, y=RT_Trial,color = Saliency))+
  geom_violin(alpha=0.2, position = position_dodge(1))+
  geom_jitter(alpha = 0.3, aes(color=Saliency), position = position_jitterdodge(.5))+
  geom_point(data = Exp1data, mapping = aes(x=validity, y=Outlier), type = "p", pch = 23, col = "cyan4", fill = "cyan4")+
  ggtitle("Distribution of RTs with outliers marked")+
  theme_bw()

```
## **ANOVA calculations**

* Analysing the data with the **individual farouts** being removed. Dependant variable is the Reaction Time and the main effects of validity and saliency are analysed along with the interaction

```{r}
anova_ifo <- ezANOVA(data = Exp1.aggdata_ifo,
                    dv = RT_Trial_ifo,
                    wid = Subject,
                    within = .(Saliency,validity),
                    detailed = TRUE)

```
The results of the ANOVA 
```{r}
anova_out(anova_ifo)
```

With 26 participants the p value for validity is 0.06 (farouts) and the interaction between saliency and validity is .17 


To check how the error ates differ the ANOVa and graphs are given below
```{r}
#ANOVA analysis for error rates
anova_ER <- ezANOVA(data = Exp1.aggdata_ER,
                    dv = Errorrate,
                    wid = Subject,
                    within = .(Saliency, validity),
                    detailed = TRUE)
anova_out(anova_ER)


```


Here, a dataframe is created where it contains the mean values of RT within each condition (saliency and validity)
```{r}


mean_ifo <- ezStats(data =Exp1.aggdata_ifo, 
                    dv = RT_Trial_ifo, 
                    wid = Subject, 
                    within = .(Saliency, validity)) 
```
* Performing the same ANOVa analysis with the **individual outliers** and check how it differs with the farouts

```{r}
anova_io <- ezANOVA(data = Exp1.aggdata_io,
                    dv = RT_Trial_io,
                    wid = Subject,
                    within = .(Saliency,validity),
                    detailed = TRUE)
anova_out(anova_io)
```

Checking the aggregate mean value for the RT after removing outliers
```{r}
mean_io <- ezStats(data =Exp1.aggdata_io, 
                    dv = RT_Trial_io, 
                    wid = Subject, 
                    within = .(Saliency, validity)) 
```
Mean value of error rates 

```{r}
mean_ER <- ezStats(data = Exp1.aggdata_ER,
                   dv=Errorrate,
                   wid = Subject,
                   within = .(Saliency,validity))
```


### Plotting the interaction 

1. Plot with Farouts removed
```{r}
## plotting the interaction with farouts
ggplot(mean_ifo, aes(x=Saliency, color=validity, y=Mean))+
  geom_line(aes(group=validity))+
  geom_point()+
  ylim(470,500)+
  labs(x="Saliency", y = "ReactionTime")+
  theme_classic()+
  ggtitle("Mean of RTs for valid and invalid trials")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.title = element_text(size=14), legend.text= element_text(size=12))+
  theme(axis.title = element_text(size=14),axis.text = element_text(size=12))
```

2. Plot with outliers removed
```{r}
ggplot(mean_io, aes(x=Saliency, color=validity, y=Mean))+
  geom_line(aes(group=validity))+
  geom_point()+
  ylim(450,500)+
  labs(x="Saliency", y = "ReactionTime")+
  theme_classic()+
  ggtitle("Mean of RTs(outliers) for valid and invalid trials")
```

3. Plot showing Error rates for validity and saliency
```{r}
ggplot(Exp1.aggdata_ER, aes(x=validity, color=Saliency, y=Errorrate))+
  geom_line(aes(group=Saliency))+
  geom_point()+
  ylim(0,30)+
  labs(x="validity", y = "ErrorRate")+
  theme_bw()+
  ggtitle("ErrorRates for valid and invalid trials")
```
Creating aplot to show the mean difference effect.
1. Subtract mean values of valid and invalid trials for salient condition and non salient condition
2. So x axis will have saliency and y axis will have mean difference

```{r}
mean_effect <- reshape(mean_ifo, direction = "wide", timevar = "validity", idvar = "Saliency")
mean_effect$Meandiff <- mean_effect$Mean.invalid - mean_effect$Mean.valid
```

#### *Plot to show the effect*

```{r}
ggplot(mean_effect, aes(x= Saliency, y = Meandiff, fill = Saliency))+
  geom_bar(stat = "identity")+
  ylim(0,10)+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(x = "Saliency", y=" Mean RT Difference between valid and invalid Trials")+
  ggtitle("Mean difference between invalid and valid trials across Saliency")
```


#### *Heres's a plot that shows the interaction*
```{r interactionplot}

ezPlot(data = Exp1.aggdata_ifo, 
       dv = RT_Trial_ifo, 
       wid = Subject, 
       within = .(Saliency,validity), 
       x=validity, levels = list(validity = list(new_order = c('valid', 'invalid'))),
       row =Saliency,
)

```


### **Plot with means**

This is a different representation of the RT to check how the mean looks like and from the looks of it, participants are fastest while responding to valid salient trials. 
```{r barplot, fig.width=8, fig.height=6}
ggplot(Exp1.aggdata_io)+
  aes(x= validity, y = RT_Trial_io, fill = Saliency) +
  geom_boxplot(alpha = .2, position = position_dodge())+
  geom_jitter(alpha = .5, aes(fill=Saliency), position = position_jitterdodge())+
  labs(x="Validity", y = "Reaction time in ms")+
  ggtitle("Mean RTs for valid and invalid trials between salient conditions")+
  theme_bw()
```






#### Removing trials where there was stimulus repetition
```{r}
Exp1data$RT_Trial_SR <- Exp1data$RT_Trial_ifo
Exp1data$RT_Trial_SR[Exp1data$PrevOccurence == "immediate"]<-NA
#removing learning trials to analyze ANOVA 
Exp1data$RT_Trial_SR[Exp1data$Condition=="learn"]<-NA
summary(Exp1data$RT_Trial_SR)
```
##ANOVA after stimulus repeated trials are controlled for
```{r}
aggdata_stimrep <- aggregate(data = Exp1data, RT_Trial_ifo~Subject+validity+Saliency,mean)
aggdata_stimrep$Subject <- as.factor(aggdata_stimrep$Subject)
aggdata_stimrep$Saliency <- as.factor(aggdata_stimrep$Saliency)
#anova calc
anova_stimrep <- ezANOVA(data=aggdata_stimrep,
                         dv=RT_Trial_ifo,
                         wid=Subject,
                         within = .(Saliency, validity),
                         detailed = TRUE)
anova_out(anova_stimrep)

```
##Plotting the means 

```{r}
mean_Stimrep <- ezStats(data = aggdata_stimrep,
                        dv = RT_Trial_ifo, 
                        wid = Subject, 
                        within = .(Saliency, validity))

ggplot(mean_Stimrep, aes(x=validity, color=Saliency, y=Mean))+
  geom_line(aes(group=Saliency))+
  geom_point()+
  ylim(470,500)+
  labs(x="validity", y = "ReactionTime")+
  theme_classic()+
  ggtitle("Main effect of validity after removing StimRep trials")


```


