# **Preliminary Analysis of Exp1-Overshadowing**
#### 14th Feb 2020
*Mrudula*


Loading the libraries and setting up working directory
```{r Libraryloading, message=FALSE}
library(plyr)
library(tidyverse)
library(ez)
library(schoRsch)
library(lme4)
library(nlme)
library(data.table)

#removing workspace objects
rm(list = ls())
setwd("D:/PhD/Exp1-Overshadowing/Analysis")
```

Then the dataframe is loaded from the directory 
```{r}
Exp1data <- read.csv("D:/PhD/Exp1-Overshadowing/Data/Exp1data.csv")
#removing the first column named x
Exp1data <- subset(Exp1data, select = -c(X))
#renaming first column to subject
names(Exp1data)[1] <- "Subject"
```

Preparing the data frame
* Creating two columns that contains the RT and ACC values
* Creating a new column with error rates
* Removing the values from the practic trials
```{r}
#creating 2 columns for RT and ACC
Exp1data$RT_Trial <- Exp1data$ExpDisplay.RT
Exp1data$ACC_Trial <- Exp1data$ExpDisplay.ACC
Exp1data$Errorrate <- 1 - Exp1data$ACC_Trial

#removing practice trials
Exp1data <- Exp1data[!grepl("Practice", Exp1data$Condition),]
```

For ANOVA analysis to check for effect of salience and validity on test trials, learn trials are not required, hence removed
```{r}
 Exp1data <- Exp1data[!grepl("learn", Exp1data$Condition),]
```

Below you can find the summary of the Reaction Time data and calculating error percentage
```{r}
summary(Exp1data$RT_Trial)
table(Exp1data$ACC_Trial)
round(table(Exp1data$ACC_Trial)/nrow(Exp1data)*100, digits = 3)
```

### Removing RTs and Outliers

Outliers are computed on an individual level 

> Separate columns are created to modify RT values of individual farouts and individual outliers instead of changing it in the original RT_Trial column

Updated summary values after removing outliers/farouts are given below
```{r}
#removing the RT of the trials that were inaccurate
Exp1data$RT_Trial[Exp1data$ACC_Trial==0] <- NA

#summary after removing incorrect trials
summary(Exp1data$RT_Trial)

#OUtliers
#creating function to remove outliers and farouts
computeTukeys <- function(x){
  P25 <- quantile(x$RT, .25, na.rm = TRUE, type = 6) #type = 6 -> nimmt SPSS
  P75 <- quantile(x$RT, .75, na.rm = TRUE, type = 6)
  x$Outlier <- P75 + 1.5*(P75 - P25)
  x$Farouts <- P75 + 3.0*(P75 - P25)
  return(x)
}

#identifying RT farouts in the individual level
Exp1data <- ddply(Exp1data, .(Subject), computeTukeys)
summary(Exp1data$RT_Trial)

#creating new column with RT trials after removing outliers
Exp1data$RT_Trial_ifo <- Exp1data$RT_Trial
Exp1data$RT_Trial_io <- Exp1data$RT_Trial
Exp1data$RT_Trial_ifo[Exp1data$RT_Trial_ifo > Exp1data$Farouts|Exp1data$RT_Trial_ifo < 300] <- NA
Exp1data$RT_Trial_io[Exp1data$RT_Trial_io > Exp1data$Outlier|Exp1data$RT_Trial_io < 300] <- NA
summary(Exp1data$RT_Trial_ifo)
summary(Exp1data$RT_Trial_io)
```
Now, a dataframe is created that contains aggregate values of the RT per condition 
```{r}
Exp1.aggdata_ifo <- aggregate(data=Exp1data, RT_Trial_ifo~Subject+Saliency+validity, mean)
Exp1.aggdata_io <- aggregate(data=Exp1data, RT_Trial_io~Subject+Saliency+validity, mean)

## changing the variables to factors for ANOVA analysis
Exp1.aggdata_io$Subject <- as.factor(Exp1.aggdata_io$Subject)
Exp1.aggdata_io$Saliency <- as.factor(Exp1.aggdata_io$Saliency)
Exp1.aggdata_io$validity <- as.factor(Exp1.aggdata_io$validity)
```

## **ANOVA calculations**

Analysing the data with the individual farouts being removed. Dependant variable is the Reaction Time and the main effects of validity and saliency are analysed along with the interaction

```{r}
anova_io <- ezANOVA(data = Exp1.aggdata_io,
                    dv = RT_Trial_io,
                    wid = Subject,
                    within = .(Saliency,validity),
                    detailed = TRUE)
```
The results of the ANOVA 
```{r}
anova_out(anova_io)
```

With 22 participants the p value has increased to .094 (farouts) and .147 (outliers) 

#### *Heres's a plot that shows the interaction*
```{r interactionplot, fig.width=8, fig.height=6}
ezPlot(data = Exp1.aggdata_io, 
       dv = RT_Trial_io, 
       wid = Subject, 
       within = .(Saliency,validity), 
       x=validity, levels = list(validity = list(new_order = c('valid', 'invalid'))),
       row =Saliency,
)

```

Here, a dataframe is created where it contains the mean values of RT within each condition (saliency and validity)
```{r}

mean_ifo <- ezStats(data =Exp1.aggdata_ifo, 
                    dv = RT_Trial_ifo, 
                    wid = Subject, 
                    within = .(Saliency, validity)) 
```
### **Plot with means**

This is a different representation of the RT to check how the mean looks like and from the looks of it, participants are fastest while responding to valid salient trials. 
```{r barplot, fig.width=8, fig.height=6}
ggplot(Exp1.aggdata_io)+
  aes(x= validity, y = RT_Trial_io, fill = Saliency) +
  geom_boxplot(alpha = .2, position = position_dodge())+
  geom_jitter(alpha = .5, aes(fill=Saliency), position = position_jitterdodge())+
  labs(x="Validity", y = "Reaction time in ms")+
  ggtitle("Mean RTs for valid and invalid trials between salient conditions")+
  theme_bw()
```

Controlling for stimulus repetition
```{r}

summary(Exp1data$RT_Trial)
Exp1data$stimRep<-ifelse(shift(Exp1data$Distractor1, n = 1, type = "lag") == Exp1data$Distractor1, 1, 0)
    table(Exp1data$stimRep)
    
    #exclude stim rep trials from CL data
    
    Exp1data$RT_Trial[Exp1data$stimRep==1] <- NA
    summary(Exp1data$RT_Trial)
    #total NA's (ifo): 2711
    
    #aggregate####
    data.agg <- aggregate(data = Exp1data, RT_Trial ~ Saliency + validity + Subject, mean)
```

Anova after removing stimulus repeated trials
```{r}
    data.agg$Subject <- as.factor(data.agg$Subject)    
    data.agg$Saliency <- as.factor(data.agg$Saliency) 
    
Anova_SRB <- ezANOVA(data = data.agg,
                     dv = RT_Trial,
                     wid = Subject,
                     within = .(Saliency, validity),
                     detailed = TRUE)
anova_out(Anova_SRB)
                     
```

